\Large On-Shell Methods for Tree-Level Amplitudes in (De)Constructed Gauge Theory

### 2025-06-05 MasterDefense/main.tex
New

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{slashed}
\usepackage[most]{tcolorbox}
\tcbset{
  thickitembox/.style={
    colback=white,
    colframe=white,
    left=2mm,
    before skip=4pt,
    after skip=4pt,
    borderline west={3pt}{0pt}{gray},  % ← 这里控制线条粗细和颜色
    enhanced,
  }
}
\setlist[itemize]{label=\textbullet}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\setlength{\parskip}{0.3em}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\sket}[1]{|#1]}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[Application of BCFW]{Tree level scattering amplitude in (De)constructed gauge theory}
\author{Su Yingze}
\institute{Nagoya University}
\date[4 21st 2025]{April 21st 2025}

\begin{document}
\frame{\titlepage}
\section{Why we need new method?}
\begin{frame}
    \frametitle{Why we need new method?}
Feynman diagram is a brilliant method without doubt, helping us compute the scattering process pertubatively.
\begin{center}

@@

\end{tikzpicture}
\end{center}
\vspace{-2.3em}
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

%Shape: Spring [id:dp43786797179465176] 
\draw   (216.4,104.97) .. controls (219.03,103.2) and (222.94,102.68) .. (226.33,106.02) .. controls (233.1,112.72) and (224.24,121.49) .. (220.86,118.14) .. controls (217.47,114.8) and (226.33,106.02) .. (233.1,112.72) .. controls (239.87,119.41) and (231.01,128.19) .. (227.63,124.84) .. controls (224.24,121.49) and (233.1,112.72) .. (239.87,119.41) .. controls (246.64,126.11) and (237.78,134.88) .. (234.4,131.53) .. controls (231.01,128.19) and (239.87,119.41) .. (246.64,126.11) .. controls (253.41,132.8) and (244.56,141.58) .. (241.17,138.23) .. controls (237.78,134.88) and (246.64,126.11) .. (253.41,132.8) .. controls (254.2,133.59) and (254.78,134.4) .. (255.18,135.22) ;
%Shape: Ellipse [id:dp10564067273276767] 
\draw  [fill={rgb, 255:red, 196; green, 189; blue, 189 }  ,fill opacity=1 ] (252.25,146.07) .. controls (252.25,135.17) and (261.17,126.33) .. (272.19,126.33) .. controls (283.2,126.33) and (292.12,135.17) .. (292.12,146.07) .. controls (292.12,156.97) and (283.2,165.8) .. (272.19,165.8) .. controls (261.17,165.8) and (252.25,156.97) .. (252.25,146.07) -- cycle ;
%Shape: Spring [id:dp8051072896719512] 
\draw   (202.57,146.94) .. controls (203.45,144.19) and (206.11,141.62) .. (210.87,142.09) .. controls (220.4,143.03) and (219.26,154.27) .. (214.5,153.79) .. controls (209.74,153.32) and (210.87,142.09) .. (220.4,143.03) .. controls (229.92,143.98) and (228.78,155.21) .. (224.02,154.74) .. controls (219.26,154.27) and (220.4,143.03) .. (229.92,143.98) .. controls (239.44,144.92) and (238.31,156.15) .. (233.54,155.68) .. controls (228.78,155.21) and (229.92,143.98) .. (239.44,144.92) .. controls (248.97,145.87) and (247.83,157.1) .. (243.07,156.63) .. controls (238.31,156.15) and (239.44,144.92) .. (248.97,145.87) .. controls (250.08,145.98) and (251.05,146.23) .. (251.89,146.59) ;
%Shape: Spring [id:dp24229359788253813] 
\draw   (291.38,147.82) .. controls (292.02,144.73) and (294.46,141.66) .. (299.24,141.73) .. controls (308.81,141.87) and (308.63,154.27) .. (303.84,154.2) .. controls (299.06,154.13) and (299.24,141.73) .. (308.81,141.87) .. controls (318.38,142.01) and (318.2,154.41) .. (313.41,154.34) .. controls (308.63,154.27) and (308.81,141.87) .. (318.38,142.01) .. controls (327.95,142.15) and (327.77,154.55) .. (322.98,154.48) .. controls (318.2,154.41) and (318.38,142.01) .. (327.95,142.15) .. controls (337.52,142.28) and (337.34,154.69) .. (332.55,154.62) .. controls (327.77,154.55) and (327.95,142.15) .. (337.52,142.28) .. controls (338.64,142.3) and (339.63,142.49) .. (340.49,142.8) ;
%Shape: Spring [id:dp1840306550125722] 
\draw   (290.58,139.13) .. controls (289.05,136.36) and (288.91,132.46) .. (292.6,129.45) .. controls (299.99,123.43) and (307.96,133) .. (304.26,136.01) .. controls (300.57,139.02) and (292.6,129.45) .. (299.99,123.43) .. controls (307.38,117.41) and (315.35,126.98) .. (311.65,129.99) .. controls (307.96,133) and (299.99,123.43) .. (307.38,117.41) .. controls (314.77,111.38) and (322.73,120.96) .. (319.04,123.97) .. controls (315.35,126.98) and (307.38,117.41) .. (314.77,111.38) .. controls (322.16,105.36) and (330.12,114.94) .. (326.43,117.95) .. controls (322.73,120.96) and (314.77,111.38) .. (322.16,105.36) .. controls (323.02,104.66) and (323.9,104.17) .. (324.76,103.85) ;
%Shape: Spring [id:dp21851269782703253] 
\draw   (271.73,127.44) .. controls (268.6,126.81) and (265.5,124.41) .. (265.56,119.67) .. controls (265.68,110.2) and (278.2,110.35) .. (278.14,115.09) .. controls (278.08,119.82) and (265.56,119.67) .. (265.68,110.2) .. controls (265.79,100.73) and (278.32,100.88) .. (278.26,105.61) .. controls (278.2,110.35) and (265.68,110.2) .. (265.79,100.73) .. controls (265.91,91.25) and (278.44,91.4) .. (278.38,96.14) .. controls (278.32,100.88) and (265.79,100.73) .. (265.91,91.25) .. controls (266.03,81.78) and (278.55,81.93) .. (278.5,86.67) .. controls (278.44,91.4) and (265.91,91.25) .. (266.03,81.78) .. controls (266.04,80.67) and (266.23,79.69) .. (266.54,78.84) ;
%Shape: Spring [id:dp05024762380258474] 
\draw   (224.2,195.95) .. controls (222.44,193.32) and (221.96,189.44) .. (225.37,186.13) .. controls (232.21,179.5) and (240.98,188.36) .. (237.56,191.68) .. controls (234.14,194.99) and (225.37,186.13) .. (232.21,179.5) .. controls (239.05,172.87) and (247.82,181.73) .. (244.4,185.05) .. controls (240.98,188.36) and (232.21,179.5) .. (239.05,172.87) .. controls (245.88,166.24) and (254.65,175.1) .. (251.24,178.42) .. controls (247.82,181.73) and (239.05,172.87) .. (245.88,166.24) .. controls (252.72,159.61) and (261.49,168.47) .. (258.07,171.79) .. controls (254.65,175.1) and (245.88,166.24) .. (252.72,159.61) .. controls (253.52,158.83) and (254.35,158.27) .. (255.18,157.88) ;
%Shape: Spring [id:dp9217960437924791] 
\draw   (283.39,161.81) .. controls (286.03,160.03) and (289.94,159.51) .. (293.32,162.86) .. controls (300.09,169.56) and (291.24,178.33) .. (287.85,174.98) .. controls (284.47,171.64) and (293.32,162.86) .. (300.09,169.56) .. controls (306.86,176.25) and (298.01,185.03) .. (294.62,181.68) .. controls (291.24,178.33) and (300.09,169.56) .. (306.86,176.25) .. controls (313.63,182.95) and (304.78,191.72) .. (301.39,188.37) .. controls (298.01,185.03) and (306.86,176.25) .. (313.63,182.95) .. controls (320.4,189.64) and (311.55,198.42) .. (308.17,195.07) .. controls (304.78,191.72) and (313.63,182.95) .. (320.4,189.64) .. controls (321.2,190.43) and (321.78,191.24) .. (322.17,192.06) ;

% Text Node
\draw (254.1,174.78) node [anchor=north west][inner sep=0.75pt]    {$\cdots $};
% Text Node
\draw (354,136) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont Can we really compute this by hand?}};

\end{frame}
\begin{frame}
    \frametitle{From Frynman diagram to On-shell method}
    The answer is On-shell method.
    \begin{center}

@@

@@

    \end{center}

    On-shell here means that all quantities we use are gauge invariant and satisfy the on-shell condition.
    Specifically, there are many ingredients under this frame
    \begin{itemize}
        \item The analytic continuation for S-matrix.
        \item The color-ordered amplitudes.
        \item The BCFW recursion relation.
        \item The spinor helicity discription for amplitudes.
    \end{itemize}
\end{frame}
\section{Preliminary}
\begin{frame}
    \frametitle{A brief introduction to BCFW}
BCFW helps us solve one of the problems
\vspace{-1em}
\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{BCFW.png}
\end{figure}
\vspace{-1em}
with the cost of introducing \textcolor{red}{complexed momentum}.

BCFW is a method to compute amplitudes recursively, proposed by 
\begin{itemize}
    \item Britto, Cachazo, Feng, arXiv: hep-th/0412308
    \item Britto, Cachazo, Feng, Witten, arXiv: hep-th/0501052

\end{itemize}

\begin{center}

 %Shape: Ellipse [id:dp47704771803228196] 
 \draw  [fill={rgb, 255:red, 158; green, 158; blue, 158 }  ,fill opacity=1 ] (179.79,126.94) .. controls (179.79,120.82) and (184.73,115.86) .. (190.81,115.86) .. controls (196.89,115.86) and (201.82,120.82) .. (201.82,126.94) .. controls (201.82,133.06) and (196.89,138.02) .. (190.81,138.02) .. controls (184.73,138.02) and (179.79,133.06) .. (179.79,126.94) -- cycle ;
 %Straight Lines [id:da8859462256956995] 
 \draw    (163,96.75) -- (182.27,118.91) ;
 %Straight Lines [id:da980370255241411] 
 \draw    (201.82,126.94) -- (232.38,126.66) ;
 %Straight Lines [id:da41368612060172827] 
 \draw    (182.82,135.52) -- (165.75,153.25) ;
 %Right Arrow [id:dp6770308298589597] 
 \draw   (240.37,124.24) -- (254.74,124.24) -- (254.74,121.68) -- (264.32,126.8) -- (254.74,131.92) -- (254.74,129.36) -- (240.37,129.36) -- cycle ;
 %Shape: Ellipse [id:dp9789947232756657] 
 \draw  [fill={rgb, 255:red, 158; green, 158; blue, 158 }  ,fill opacity=1 ] (277.26,126.94) .. controls (277.26,120.82) and (282.19,115.86) .. (288.27,115.86) .. controls (294.35,115.86) and (299.28,120.82) .. (299.28,126.94) .. controls (299.28,133.06) and (294.35,138.02) .. (288.27,138.02) .. controls (282.19,138.02) and (277.26,133.06) .. (277.26,126.94) -- cycle ;
 %Straight Lines [id:da15853752019875] 
 \draw    (263.22,98.41) -- (279.74,118.91) ;
 %Straight Lines [id:da28595275955528565] 
 \draw    (299.28,126.94) -- (329.84,126.66) ;
 %Straight Lines [id:da7505788363123894] 
 \draw    (280.29,135.52) -- (263.22,153.25) ;
 %Shape: Ellipse [id:dp870376485686725] 
 \draw  [fill={rgb, 255:red, 158; green, 158; blue, 158 }  ,fill opacity=1 ] (351.87,126.66) .. controls (351.87,120.54) and (346.94,115.58) .. (340.86,115.58) .. controls (334.77,115.58) and (329.84,120.54) .. (329.84,126.66) .. controls (329.84,132.78) and (334.77,137.74) .. (340.86,137.74) .. controls (346.94,137.74) and (351.87,132.78) .. (351.87,126.66) -- cycle ;
 %Straight Lines [id:da5791423310908868] 
 \draw    (363.43,98.97) -- (349.94,118.91) ;
 %Straight Lines [id:da5454664407915119] 
 \draw    (349.43,134.42) -- (365.28,152.14) ;
 %Right Arrow [id:dp848095583389827] 
 \draw   (368.11,124.79) -- (382.49,124.79) -- (382.49,122.23) -- (392.07,127.35) -- (382.49,132.48) -- (382.49,129.92) -- (368.11,129.92) -- cycle ;

 % Text Node
 \draw (393.76,120.95) node [anchor=north west][inner sep=0.75pt]    {$\cdots $};

@@

\end{frame}
\begin{frame}
    \frametitle{From real to complex -- Analytic Continuation}
    \textbf{Why can we conduct analytic continuation?}
\begin{itemize}
  \item Tree level scattering amplitudes are rational functions of Lorentz invariants, such as $\bm{p_{i\mu}p_j^\mu}$, $\bm{p_{i\mu}\epsilon_j^\mu}$.
  \item \textbf{Locality} tells us that any pole of a tree-level amplitude must correspond to a on-shell propagating particle. 
  \item There's only single pole, no branch cuts (logs, square roots, etc) at tree level.
\end{itemize}
    \begin{center}
    \tikz{
      \draw[double equal sign distance, -Implies, line width=1pt] (0,0) -- (0,-1.2);
    }
    \end{center}
\vspace{0.5em}
\centering
\textcolor{red}{Amplitudes can be shifted to complex plane}
\end{frame}

\begin{frame}
    \frametitle{Momentum Shift in BCFW}
    \textbf{What did BCFW do to make the shift?}

    Here we consider the case in which all particles are massless, $p_i^2 = 0$ for all $i = 1, 2, \dotsc, n$. We choose two momentum to be shifted oppositely 
    \begin{equation*}
        p_i\rightarrow\hat{p}_i(z)\equiv p_i-zk,\qquad p_j\rightarrow\hat{p}_j(z)\equiv p_j+zk
    \end{equation*}
    satisfying 
    \begin{equation*}
        k^2=0,\qquad p_i\cdot k=0,\qquad p_j\cdot k=0
    \end{equation*}

\begin{figure}
    \centering
    \begin{minipage}{0.45\textwidth}
        \tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[scale=0.7,x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Shape: Circle [id:dp47058391497271046] 
\draw  [fill={rgb, 255:red, 151; green, 145; blue, 145 }  ,fill opacity=1 ] (266.75,126) .. controls (266.75,112.19) and (277.94,101) .. (291.75,101) .. controls (305.56,101) and (316.75,112.19) .. (316.75,126) .. controls (316.75,139.81) and (305.56,151) .. (291.75,151) .. controls (277.94,151) and (266.75,139.81) .. (266.75,126) -- cycle ;
%Straight Lines [id:da8759716500759761] 
\draw    (249,78.25) -- (273.5,109.25) ;
%Straight Lines [id:da2121821831988906] 
\draw    (233.5,103.25) -- (266.5,120.75) ;
%Straight Lines [id:da6378763431676462] 
\draw  [dash pattern={on 0.84pt off 2.51pt}]  (350.75,54.38) -- (350.75,126.25) -- (350.75,187.63) ;
%Straight Lines [id:da7508961107891289] 
\draw  [dash pattern={on 0.84pt off 2.51pt}]  (248.25,124) -- (248.5,142.25) ;
%Straight Lines [id:da06317949320750826] 
\draw    (237,155.25) -- (271.5,140.75) ;
%Straight Lines [id:da403008866951158] 
\draw    (261.5,180.25) -- (281.5,149.25) ;
%Straight Lines [id:da8334043101335312] 
\draw    (423,119.25) -- (457.5,104.75) ;
%Straight Lines [id:da03451573841415356] 
\draw    (418.5,109.75) -- (438.5,78.75) ;
%Straight Lines [id:da025418352459996796] 
\draw    (420,140.25) -- (453,157.75) ;
%Straight Lines [id:da22879254297825424] 
\draw  [dash pattern={on 0.84pt off 2.51pt}]  (442.25,121) -- (442.5,139.25) ;
%Straight Lines [id:da2355772127149045] 
\draw    (410.5,148.75) -- (435,179.75) ;
%Shape: Rectangle [id:dp6752662310096104] 
\draw   (328,54.25) -- (328,198.75) -- (212,198.75) -- (212,54.25) -- cycle ;
%Straight Lines [id:da4580921639862495] 
\draw    (316.75,126) -- (373.5,125.75) ;
%Shape: Circle [id:dp8699671429684472] 
\draw  [fill={rgb, 255:red, 151; green, 145; blue, 145 }  ,fill opacity=1 ] (373.5,125.75) .. controls (373.5,111.94) and (384.69,100.75) .. (398.5,100.75) .. controls (412.31,100.75) and (423.5,111.94) .. (423.5,125.75) .. controls (423.5,139.56) and (412.31,150.75) .. (398.5,150.75) .. controls (384.69,150.75) and (373.5,139.56) .. (373.5,125.75) -- cycle ;

% Text Node
\draw (239.75,58.4) node [anchor=north west][inner sep=0.75pt]    {$\hat{i}$};
% Text Node
\draw (447.47,58.4) node [anchor=north] [inner sep=0.75pt]    {$\hat{j}$};
% Text Node
\draw (250.75,177.9) node [anchor=north west][inner sep=0.75pt]    {$n$};
% Text Node
\draw (224.25,147.4) node [anchor=north west][inner sep=0.75pt]    {$1$};
% Text Node
\draw (424.25,176.9) node [anchor=north west][inner sep=0.75pt]    {$n-1$};
% Text Node
\draw (268.75,34.4) node [anchor=north west][inner sep=0.75pt]  [color={rgb, 255:red, 241; green, 12; blue, 12 }  ,opacity=1 ]  {$I$};

\end{tikzpicture}
    \end{minipage}
    \hspace{1em}
    \begin{minipage}{0.45\textwidth}
        For a non-trival subset of generic momenta $\{p_i\}_{i\in I}$
    \begin{equation*}
        \hat{P}_I^2=P_I^2 -2zP_I\cdot k=-\frac{P_I^2}{z_I}(z-z_I) 
    \end{equation*}

    with $\textcolor{red}{\quad z_I=\frac{P_I^2}{2P_I\cdot k}}$.  
    \end{minipage}
\end{figure} 
\end{frame}

\begin{frame}
    \frametitle{Fantasitic result from Cauchy Theorem}
    %First, I will show the most important part in this report.
    \begin{block}{BCFW recursion relation}
        \begin{equation*}
            A_n=\sum_{\text{diagrams}\,I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)=\sum_{\text{diagrams}\,I}\raisebox{-1.3em}{\includegraphics[height=3em]{recrel1.pdf}}
        \end{equation*}
    \end{block}
    Brief proof:

    We consider amplitude $A_n$ in terms of shifted momentum $\hat{p}_i^\mu$ instead of original real momentum. 
    \begin{equation*}
        A_n \longrightarrow \hat{A}_n(z)
    \end{equation*}

>>>>

\documentclass{beamer}
\usetheme{Madrid}
\usefonttheme{professionalfonts}
\usecolortheme{rose}
\usepackage{fontspec}
\setmainfont{Times New Roman}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tikz}
\usepackage{svg}
\usepackage{graphics}
\usepackage{appendixnumberbeamer}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{comment}
\usepackage{slashed}
\usepackage[most]{tcolorbox}

\setlist[enumerate]{label=\arabic*.}
\setlist[itemize]{label=\textbullet}  % 标准 bullet 点
\tcbset{
  thickitembox/.style={
    colback=white,
    colframe=white,
    left=2mm,
    before skip=4pt,
    after skip=4pt,
    borderline west={3pt}{0pt}{gray},  % ← 这里控制线条粗细和颜色
    enhanced,
  }
}
\usetikzlibrary{decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\setlength{\parskip}{0.3em}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\sket}[1]{|#1]}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
\newcommand{\tif}[1]{\textit{\textbf{#1}}}
\AtBeginSection[]{
\begin{frame} 
    \frametitle{Contents}
    \tableofcontents[currentsection]
\end{frame}
}
\title[Application of BCFW]{\Large On-Shell Methods for Tree-Level Amplitudes in (De)Constructed Gauge Theory}
\author[Su Yingze]{
  \textbf{Su Yingze}\\[0.2em]
  \small Supervisor: \tif{Prof. Tanabashi Masaharu}
}

\institute[E Lab]{
  \normalsize Theoretical Elementary Particle Physics Laboratory\\[-0.3em]
  Nagoya University
}

\date[$11^{\text{th}}$ June]{June 11th, 2025}

\begin{document}
\setbeamertemplate{itemize item}{\normalsize\textbullet}
\begin{frame} % ← 不使用 [plain]，保留 Madrid 顶部蓝条
  \titlepage
\end{frame}
\section{Motivation}
\begin{frame}{Why We Study Scattering Amplitudes?}
  \begin{enumerate}
    \item \textbf{Bridge between theory and experiment}
    \begin{itemize}
      \item Core prediction targets for high-energy collider experiments such as the LHC
      \item Any new theory (SUSY, GUTs, extra dimensions) must predict observable cross sections
    \end{itemize}
    \pause
    \item \textbf{Reveal deep structures of quantum field theory}
    \begin{itemize}
      \item Amplitudes exhibit hidden symmetries (e.g., dual conformal, Yangian) not visible in the Lagrangian
      \item These symmetries suggest deeper theoretical frameworks, such as amplituhedra or AdS/CFT correspondence
    \end{itemize}
  \end{enumerate}
\end{frame}

\begin{frame}
    \frametitle{Challenges we face befor}
\begin{center}

@@

\end{tikzpicture}
\end{center}
\vspace{-2.3em}
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|c|}
\hline
$n=$ & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
\hline
     & 4 & 25 & 220 & 2485 & 34300 & 559405 & 10525900 \\
\hline
\end{tabular}
\end{center}
\pause

The answer is On-shell method.
    \begin{center}

@@

\end{tikzpicture}
\end{center}
\end{frame}
\section{Preliminary}
\begin{frame}
    \frametitle{Conventional VS. Modern}
    Usually, when we compute the gluon amplitudes by using Feynman diagram, we will obtain something like 
\begin{equation*}
    \begin{aligned}
&\mathcal{M}_s(p_1 p_2 \to p_3 p_4) = - \frac{g_s^2}{s} f^{abe} f^{cde} \\
&\quad \times \Big\{ 
-4\, \epsilon_1 \cdot \epsilon_3^* \, \epsilon_2 \cdot p_1 \, \epsilon_4^* \cdot p_3 
+ 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_1 \, \epsilon_4^* \cdot p_3 \\
&\quad - 2\, \epsilon_1 \cdot p_4 \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^*
+ \epsilon_1 \cdot \epsilon_2 \, p_4 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^* \\
&\quad + 4\, \epsilon_1 \cdot \epsilon_4^* \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot p_4 
- 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_4 \, \epsilon_4^* \cdot p_1 \\
&\quad - 2\, \epsilon_1 \cdot p_2 \, \epsilon_2 \cdot p_3 \, \epsilon_3^* \cdot \epsilon_4^*
+ \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot \epsilon_4^* \, p_2 \cdot p_3 \\
&\quad + 4\, \epsilon_1 \cdot p_2 \, \epsilon_2 \cdot \epsilon_3^* \, \epsilon_4^* \cdot p_3 
- 2\, \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot p_2 \, \epsilon_4^* \cdot p_3 \\
&\quad + 2\, \epsilon_1 \cdot p_2 \, \epsilon_2 \cdot p_4 \, \epsilon_3^* \cdot \epsilon_4^* 
- \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot \epsilon_4^* \, p_4 \cdot p_2 \\
&\quad + 2\, \epsilon_1 \cdot p_3 \, \epsilon_2 \cdot p_1 \, \epsilon_3^* \cdot \epsilon_4^* 
- \epsilon_1 \cdot \epsilon_2 \, \epsilon_3^* \cdot \epsilon_4^* \, p_1 \cdot p_3 
\Big\}.
\end{aligned}
\end{equation*}
\end{frame}
\begin{frame}
    If you consider 5point case, it will become worser:
\begin{center}
    \textcolor{red}{$\bigstar$ There are nearly 10000 terms!}
\end{center}
\begin{columns}[T,onlytextwidth]
    % 左侧：传统图像
    \column{0.48\textwidth}
    \textbf{传统费曼图计算：}
    \begin{figure}
        \centering
        \includegraphics[width=\linewidth]{5pt.png}
    \end{figure}
    \pause 
    % 右侧：PT表达式
    \column{0.48\textwidth}
    \vspace{1.5em}
    \qquad \textbf{Parke–Taylor Formula:}
    \begin{gather*}
        \textcolor{red}{A_5(1^-,2^-,3^+,4^+,5^+)} =\\
        \textcolor{red}{\frac{\langle 1 2 \rangle^4}{\langle 1 2 \rangle \langle 2 3 \rangle \langle 3 4 \rangle \langle 4 5 \rangle \langle 5 1 \rangle}}
    \end{gather*}
\end{columns}
\vspace{2em}
\textcolor{red}{$\bigstar$ \Large It becomes quite simple and compact!}
\end{frame}
\begin{frame}
    \frametitle{Fantasitic result from Cauchy Theorem}
    %First, I will show the most important part in this report.
    \begin{block}{BCFW recursion relation}
        \begin{equation*}
            A_n=\sum_{\text{diagrams}\,I}\hat{A}_L(z_I)\frac{1}{P_I^2}\hat{A}_R(z_I)=\sum_{\text{diagrams}\,I}\raisebox{-1.3em}{\includegraphics[height=3em]{recrel1.pdf}}
        \end{equation*}
    \end{block}
\vspace*{1em}
\pause
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

%Shape: Circle [id:dp714548377068662] 
\draw  [fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=1 ] (226.5,142.5) .. controls (226.5,135.6) and (232.1,130) .. (239,130) .. controls (245.9,130) and (251.5,135.6) .. (251.5,142.5) .. controls (251.5,149.4) and (245.9,155) .. (239,155) .. controls (232.1,155) and (226.5,149.4) .. (226.5,142.5) -- cycle ;
%Straight Lines [id:da2774899580018806] 
\draw    (205.75,111.25) -- (228.5,135) ;
%Straight Lines [id:da9722977180083648] 
\draw    (206.25,170.75) -- (229.5,151.5) ;
%Straight Lines [id:da6995788762725553] 
\draw    (283,142.5) -- (251.5,142.5) ;
%Shape: Circle [id:dp5472781658369114] 
\draw  [fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=1 ] (338.5,142) .. controls (338.5,135.1) and (344.1,129.5) .. (351,129.5) .. controls (357.9,129.5) and (363.5,135.1) .. (363.5,142) .. controls (363.5,148.9) and (357.9,154.5) .. (351,154.5) .. controls (344.1,154.5) and (338.5,148.9) .. (338.5,142) -- cycle ;
%Straight Lines [id:da00014298672423462833] 
\draw    (317.75,110.75) -- (340.5,134.5) ;
%Straight Lines [id:da9890078833503395] 
\draw    (317.25,169.75) -- (341.5,151) ;
%Straight Lines [id:da6144558640267263] 
\draw    (395,142) -- (363.5,142) ;
%Right Arrow [id:dp2461212615941556] 
\draw  [fill={rgb, 255:red, 241; green, 80; blue, 80 }  ,fill opacity=1 ] (289.75,140.31) -- (304.3,140.31) -- (304.3,138.25) -- (314,142.38) -- (304.3,146.5) -- (304.3,144.44) -- (289.75,144.44) -- cycle ;
%Shape: Circle [id:dp17520461351076555] 
\draw  [fill={rgb, 255:red, 155; green, 155; blue, 155 }  ,fill opacity=1 ] (395,142) .. controls (395,135.1) and (400.6,129.5) .. (407.5,129.5) .. controls (414.4,129.5) and (420,135.1) .. (420,142) .. controls (420,148.9) and (414.4,154.5) .. (407.5,154.5) .. controls (400.6,154.5) and (395,148.9) .. (395,142) -- cycle ;
%Straight Lines [id:da6771243917531791] 
\draw    (417.25,132.75) -- (440.25,111.75) ;
%Straight Lines [id:da9753272478311303] 
\draw    (419.25,149.75) -- (440.75,167.75) ;
%Right Arrow [id:dp8085176402619464] 
\draw  [fill={rgb, 255:red, 241; green, 80; blue, 80 }  ,fill opacity=1 ] (444.25,137.81) -- (458.8,137.81) -- (458.8,135.75) -- (468.5,139.88) -- (458.8,144) -- (458.8,141.94) -- (444.25,141.94) -- cycle ;

% Text Node
\draw (82,133.5) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont {\small More understandable:}}};
% Text Node
\draw (473.5,130.9) node [anchor=north west][inner sep=0.75pt]    {$\cdots $};
% Text Node
\draw (224,164.5) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont {\footnotesize 3 point}}};
% Text Node
\draw (363.5,162) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont {\footnotesize 4 point}}};
% Text Node
\draw (479,160) node [anchor=north west][inner sep=0.75pt]   [align=left] {{\fontfamily{ptm}\selectfont {\footnotesize higher point}}};

@@

\textcolor{red}{$\bigstar $ ~ From lower point to higher point!!}

\end{frame}
\begin{frame}{Spinor-Helicity Formalism}
\begin{block}{Helicity}
\textbf{Helicity} is defined as the projection of a particle's spin vector $\vec{S}$ onto the direction of its momentum $\vec{p}$:
\[
h = \frac{\vec{S} \cdot \vec{p}}{|\vec{p}|}
\]
\end{block}
\pause
% 文本说明（点击1出现）
\only<1->{
S-matrix is a function of momentum $p_i$ and helicity $h_i$
}

\vspace{0.8em}

% TikZ 图（点击1显示公式，点击2后补图形）
\begin{center}
\tikzset{every picture/.style={line width=0.75pt}}        
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]

  % 点击1：显示公式
  \only<1>{
    \draw (260.25,137.9) node [anchor=north west][inner sep=0.75pt] 
          {$\mathcal{M}( p_{i} ,h_{i})$};
  }

  % 点击2及后：公式 + 圈箭头
  \only<2->{
    \draw (260.25,137.9) node [anchor=north west][inner sep=0.75pt] 
          {$\mathcal{M}( p_{i} ,\textcolor{red}{h_{i}})$};

    % 圆圈
    \draw  [color=red, draw opacity=1] 
      (302.8,146.93) .. controls (302.81,142.78) and (306.18,139.44) .. (310.32,139.45)
      .. controls (314.47,139.46) and (317.81,142.83) .. (317.8,146.97)
      .. controls (317.79,151.11) and (314.42,154.46) .. (310.28,154.45)
      .. controls (306.14,154.44) and (302.79,151.07) .. (302.8,146.93) -- cycle;

    % 箭头
    \draw [color=red, draw opacity=1] 
      (310.28,154.45) -- (296.03,178.04);
    \draw [shift={(295,179.75)}, rotate=301.13, color=red, draw opacity=1][line width=0.75pt] 
      (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0)
      .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29);

    % 注释文字
    \draw (173.25,181) node [anchor=north west][inner sep=0.75pt]  
      [font=\small,color=red,opacity=1] [align=left] 
      {How can we catch the information of helicity?};
  }

@@

% 点击3：Massless Case（用 uncover 保持排版稳定）
\uncover<3->{
\vspace{-1em}
\textbf{Massless Case:}
\begin{itemize}
  \item Momenta in spinor form:
    \[
      p_{\mu}\sigma^{\mu} = p_{\alpha\dot{\alpha}} = p_\alpha \tilde{p}_{\dot{\alpha}} = \aket{p}[p|
    \]
\end{itemize}
}
